### 2012-03-25 exam4/2.tex
revise cover page

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{./exam}
\usepackage{type1cm} % We are using scalable fonts. Really.
\usepackage{alltt,times,comment,amsmath}
\usepackage{alltt}
\usepackage{ct} % tight CM font for \tt
\newexercise{exercise}{Exercise}[subsection]

@@

\ifrubric
\newenvironment{solution}{}{}
\else
\excludecomment{solution}
\fi
\newexercise{problem}{Problem}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\vspace*{-1.5cm}
\ifrubric
\centerline{\Large CSU2510H Exam 1 Rubric -- Spring 2012}

\else
\centerline{\Large CSU2510H Exam 1 -- Spring 2012}

@@

\begin{center}
\begin{tabular}{l@{\qquad}l}
Name:                        & \rule{174pt}{1pt} \\[.5cm]
Student Id (last 4 digits):  & \rule{174pt}{1pt} \\[.5cm]
%Section (morning, honors or afternoon):           & \rule{174pt}{1pt} \\[.5cm]
\end{tabular}
\end{center}

@@

\item You may write {\tt {\slshape c} $\rightarrow$ {\slshape e}} as
  shorthand for
  {\tt (check-expect {\slshape c e})}.

@@

\item The extra credit problem is \emph{all or nothing};  no partial
  credit will be awarded.

@@

\emph{Good luck!}
\end{minipage}\hfil\begin{minipage}[t]{6cm}
\rule{1cm}{0pt}\begin{tabular}{|c|l|@{/}r|}
\hline
{\bf Problem} & Points & out of \\ \hline
1 & & 18\\ \hline
2 & & 10\\ \hline
3 & & 15\\ \hline
4 & & 15\\ \hline
5 & & 18\\ \hline
Extra & & 5 \\ \hline
{\bf Total} & & 76+5 \\ \hline
%{\bf Base}  & \multicolumn{2}{l|}{{\bf 56}} \\ \hline
\end{tabular}
\end{minipage}

@@

\fi

@@

\begin{solution}
\begin{verbatim}
;;> [6 pts -- contract and purpose for each method]
;; A P implements:
;; - size : -> Number
;;   Size of this P.
;; - replace-x : String -> P
;;   Replace x field (if any) of this P with given string.
;; - same-x-and-w? : String String -> Boolean
;;   Is there a B within this P with given x field and w field?

;;> [0 pts -- not required, but write something]
;; An A implements:
;; - w : -> String
;;   Get the w string.

;;> [2 pts] In a%: 
(define (size) 5)
(define (replace-x str) this)
(define (same-x-and-w? g c) false)

;;> [3 pts] In b%:
(define (size) 8)
(define (replace-x str)
  (new b% str (this . y)))
(define (same-x-and-w? g c)
  (and (string=? g (this . x))
       (string=? c (this . y . w))))

;;> [4 pts] In c%:
(define (size) (add1 (this . z . size)))
(define (replace-x str)
  (new c% (this . z . replace-x str)))
(define (same-x-and-w? g c)
  (this . z . same-x-and-w? g c))

;; tests
;;> [3 pts -- 1 per method]

\end{verbatim}
\end{solution}
\end{problem}
%\ifrubric\bigskip\else
\newpage
%\fi

@@

\begin{solution}
\begin{verbatim}

;; [2 pts% -- class def]
(define-class list%
  ;; [2 pts -- contract and purpose]
  ;; sum-sqrs : -> Number
  ;; compute the sum of the squares of the numbers in this list
  ;; [4 pts -- implementation]
  (define (sum-sqrs)
    ((this . sqrs) . sum)))

;; [2 pts -- tests]
(check-expect ((new mt%) . sum-sqrs) 0)
\end{verbatim}
\end{solution}

@@

\begin{solution}
\begin{verbatim}
;; [1 pt -- contract & purpose]
;; pred1 : Set String -> Boolean
;; check the "insert-size" property
;; [4 pts -- code]
(define (pred1 s i)
  (= (s . insert i . size)
     (cond [(s . has? i) (add1 (s . size))]
           [else               (s . size)])))

;; [2 pts -- test case]
(check-expect (pred1 empty-set "hi") true)

;; [1 pt -- contract & purpose]
;; pred2 : Set String -> Boolean
;; check the "remove-insert" property
;; [3 pts -- code]
(define (pred2 s a b)
  (= (s . insert a . remove b . size)
     (s . remove b . insert a . size))

;; [1 pt -- successful test]
(check-expect (pred2 empty-set "yes" "no") true)

;; counter-example
;; [3 pts -- failing test]
(check-expect (pred2 empty-set "yes" "yes") true) ;; either true or false
\end{verbatim}
\end{solution}

@@

\begin{solution}
\begin{verbatim}
;;> [1pts -- interfaces, contracts, purpose]
;; An Elem implements
;; - list-files : -> LoElem
;;   List all files within this element.

;;> [2pts -- interfaces, contracts, purpose]
;; A LoElem implements
;; - list-files : -> LoElem
;;   List all files within this list of elements.
;; - append : LoElem -> LoElem
;;   Append this list of elements to given list.

;;> [1pt -- code]
;; in dir%
(define (list-files)
  (this . elems . list-files))

;;> [1pt -- code]
;; in file%
(define (list-files)
  (new cons% this (new mt%)))

;;> [2pt -- code]
;; in mt%
(define (append loe) loe)
(define (list-files) this)

;;> [4pt -- code]
;; in cons%
(define (append loe)
  (new cons% (this . first) (this . rest . append loe)))
(define (list-files)
  (this . first . list-files . append (this . rest . list-files)))

;;> [1pt -- sanity]

;;> [3pts -- tests]
;; tests
(check-expect (mt . append (new cons% a mt)) (new cons% a mt))
(check-expect ((new cons% a mt) . append (new cons% b mt))
              (new cons% a (new cons% b mt)))

@@

(check-expect (a . list-files) (new cons% a mt))
\end{verbatim}
\end{solution}

@@

@@

\begin{solution}
\begin{verbatim}
;; Part 1: [2 pts]
(define-class fact%
  (define (fact n)
    (cond [(n . zero?) one]
          [else (n . times (this . fact (n . sub1)))])))

;; Part 2:
;; [2 pts -- data defintion]
;; A Natural is one of
;; - (new zero%)
;; - (new succ% Natural)
(define-class zero%
  ;; [4 pts -- methods in zero%]
  (define (sub1) this)
  (define (plus n) n)
  (define (add1) (new succ% this))
  (define (times n) this)
  (define (zero?) true))

(define-class succ%
  (fields pred)
  ;; [7 pts -- methods in succ%]
  (define (zero?) false)
  (define (add1) (new succ% this))
  (define (plus n) (this . pred . plus n . add1))
  (define (times n) (this . pred . times n . plus n))
  (define (sub1) (this . pred)))

(define zero (new zero%))
;; [1 pt -- define one]
(define one (new succ% (new zero%)))

;; [3 pts -- tests]
(check-expect (one . zero?) false)
(check-expect (one . sub1) zero)
(check-expect ((new succ% one) . sub1) one)
(check-expect (zero . zero?) true)
(check-expect (zero . sub1) zero)
\end{verbatim}
\newpage
\end{solution}

@@

\begin{solution}
\begin{verbatim}
;; [5 pts -- get it right]
(define-class fact%
  (define (fact n)
    (n . zero? . branch (new const% one) (new recur% n))))
(define-class const%
  (fields run))
(define-class recur%
  (fields n)
  (define (run) ((new fact%) . fact (this . n . sub1) . times (this . n))))

@@

(define true (new t%)) (define false (new f%))
\end{verbatim}
\end{solution}
\end{problem}
\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{./exam}
\usepackage{type1cm} % We are using scalable fonts. Really.
\usepackage{alltt,times,comment,amsmath}
\usepackage{alltt}
\usepackage{ct} % tight CM font for \tt
\usepackage[usenames,dvipsnames]{xcolor}
\newexercise{exercise}{Exercise}[subsection]

@@

\ifrubric
\newenvironment{solution}{\color{Red}}{}
\else
\excludecomment{solution}
\fi
\newexercise{problem}{Problem}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\vspace*{-1.5cm}
\centerline{\Large CSU2510H Exam 1 \ifrubric (SOLUTION) \fi-- Spring 2012}

@@

\ifrubric\relax\else
\begin{center}
\begin{tabular}{l@{\qquad}l}
Name:                        & \rule{174pt}{1pt} \\[.5cm]
Student Id (last 4 digits):  & \rule{174pt}{1pt} \\[.5cm]
%Section (morning, honors or afternoon):           & \rule{174pt}{1pt} \\[.5cm]
\end{tabular}
\end{center}
\fi

@@

\item You may write {\tt {\slshape c} $\rightarrow$ {\slshape e}} as
  shorthand for writing both {\tt check-expect} and {\tt
    Tester.checkExpect}.

@@

% \item The extra credit problem is \emph{all or nothing};  no partial
%   credit will be awarded.

@@

\emph{Good luck!}
\end{minipage}\hfil\begin{minipage}[t]{6cm}
\rule{1cm}{0pt}\begin{tabular}{|c|l|@{/}r|}
\hline
{\bf Problem} & Points & out of \\ \hline
1 & & ??\\ \hline
2 & & ??\\ \hline
3 & & ??\\ \hline
4 & & ??\\ \hline
5 & & ??\\ \hline
%% Extra & & 5 \\ \hline
{\bf Total} & & ?? \\ \hline
%{\bf Base}  & \multicolumn{2}{l|}{{\bf 56}} \\ \hline
\end{tabular}
\end{minipage}

@@

@@

\begin{solution}
\begin{alltt}
\rubricpts{6 pts -- contract and purpose for each method}
;; A P implements:
;; - size : -> Number
;;   Size of this P.
;; - replace-x : String -> P
;;   Replace x field (if any) of this P with given string.
;; - same-x-and-w? : String String -> Boolean
;;   Is there a B within this P with given x field and w field?

\rubricpts{0 pts -- not required, but write something}
;; An A implements:
;; - w : -> String
;;   Get the w string.

\rubricpts{2 pts}
;; In a%: 
(define (size) 5)
(define (replace-x str) this)
(define (same-x-and-w? g c) false)

\rubricpts{3 pts}
;; In b%:
(define (size) 8)
(define (replace-x str)
  (new b% str (this . y)))
(define (same-x-and-w? g c)
  (and (string=? g (this . x))
       (string=? c (this . y . w))))

\rubricpts{4 pts}
;; In c%:
(define (size) (add1 (this . z . size)))
(define (replace-x str)
  (new c% (this . z . replace-x str)))
(define (same-x-and-w? g c)
  (this . z . same-x-and-w? g c))

;; tests
\rubricpts{3 pts -- 1 per method}
(define a (new a% "a"))
(define b (new b% "b" a))
(define c (new c% b))
(define d (new c% a))
(check-expect (a . size) 5)
(check-expect (b . size) 8)
(check-expect (c . size) 6)
(check-expect (d . size) 9)
(check-expect (a . replace-x "*") a)
(check-expect (b . replace-x "*") (new b% "*" a))
(check-expect (c . replace-x "*") (new c% (new b% "*" a)))
(check-expect (d . replace-x "*") d)
(check-expect (a . same-x-and-w? "b" "a") false)
(check-expect (b . same-x-and-w? "b" "a") true)
(check-expect (c . same-x-and-w? "b" "a") true)
(check-expect (d . same-x-and-w? "b" "a") false)
\end{alltt}
\end{solution}
\end{problem}
%\ifrubric\bigskip\else
\newpage
%\fi

@@

\begin{solution}
\begin{alltt}
\rubricpts{2 pts% -- class def}
(define-class list%
  \rubricpts{2 pts -- contract and purpose}
  ;; sum-sqrs : -> Number
  ;; compute the sum of the squares of the numbers in this list
  \rubricpts{4 pts -- implementation}
  (define (sum-sqrs)
    ((this . sqrs) . sum)))

\rubricpts{2 pts -- tests}
(check-expect ((new mt%) . sum-sqrs) 0)
\end{alltt}
\end{solution}

@@

\begin{solution}
\begin{alltt}
\rubricpts{1 pt -- contract & purpose}
;; check-insert-size : Set String -> Boolean
;; check the "insert-size" property on s and i.
\rubricpts{4 pts -- code}
(define (check-insert-size s i)
  (= (s . insert i . size)
     (cond [(s . has? i) (add1 (s . size))]
           [else               (s . size)])))

\rubricpts{2 pts -- test case}
(check-expect (check-insert-size empty-set "hi") true)

\rubricpts{1 pt -- contract & purpose}
;; check-remove-insert : Set String -> Boolean
;; check the "remove-insert" property on s, a, and b.
\rubricpts{3 pts -- code}
(define (check-remove-insert s a b)
  (= (s . insert a . remove b . size)
     (s . remove b . insert a . size))

\rubricpts{1 pt -- successful test}
(check-expect (check-remove-insert empty-set "yes" "no") true)

;; Property does not hold.
;; Counter-example (failing test):
\rubricpts{3 pts -- failing test}
(check-expect (check-remove-insert empty-set "yes" "yes") true)
\end{alltt}
\end{solution}

@@

\begin{solution}
\begin{alltt}
\rubricpts{1pts -- interfaces, contracts, purpose}
;; An Elem implements
;; - list-files : -> LoElem
;;   List all files within this element.

\rubricpts{2pts -- interfaces, contracts, purpose}
;; A LoElem implements
;; - list-files : -> LoElem
;;   List all files within this list of elements.
;; - append : LoElem -> LoElem
;;   Append this list of elements to given list.

\rubricpts{1pt -- code}
;; in dir%
(define (list-files)
  (this . elems . list-files))

\rubricpts{1pt -- code}
;; in file%
(define (list-files)
  (new cons% this (new mt%)))

\rubricpts{2pt -- code}
;; in mt%
(define (append loe) loe)
(define (list-files) this)

\rubricpts{4pt -- code}
;; in cons%
(define (append loe)
  (new cons% (this . first) (this . rest . append loe)))
(define (list-files)
  (this . first . list-files . append (this . rest . list-files)))

\rubricpts{1pt -- sanity}

\rubricpts{3pts -- tests}
;; tests
(check-expect (mt . append (new cons% a mt)) (new cons% a mt))
(check-expect ((new cons% a mt) . append (new cons% b mt))
              (new cons% a (new cons% b mt)))

@@

(check-expect (a . list-files) (new cons% a mt))
\end{alltt}
\end{solution}

@@

\begin{solution}
\begin{alltt}
\rubricpts{2 pts}
(define-class fact%
  (define (fact n)
    (cond [(n . zero?) one]
          [else (n . times (this . fact (n . sub1)))])))

\end{alltt}
\end{solution}

@@

\begin{solution}
\begin{alltt}
\rubricpts{2 pts -- data defintion}
;; A Natural is one of
;; - (new zero%)
;; - (new add1% Natural)
(define-class zero%
  \rubricpts{4 pts -- methods in zero%}
  (define (sub1) this)
  (define (zero?) true)
  (define (add1) (new add1% this))
  (define (plus n) n)
  (define (times n) this))

(define-class add1%
  (fields sub1)
  \rubricpts{7 pts -- methods in add1%}
  (define (zero?) false)
  (define (add1) (new add1% this))
  (define (plus n) (this . sub1 . plus n . add1))
  (define (times n) (this . sub1 . times n . plus n)))

(define zero (new zero%))
\rubricpts{1 pt -- define one}
(define one (new add1% (new zero%)))

\rubricpts{3 pts -- tests}
(check-expect (one . zero?) false)
(check-expect (one . sub1) zero)
(check-expect ((new add1% one) . sub1) one)
(check-expect (zero . zero?) true)
(check-expect (zero . sub1) zero)
\end{alltt}
\newpage
\end{solution}

@@

\begin{solution}
\begin{alltt}
\rubricpts{5 pts -- get it right}
(define-class fact%
  (define (fact n)
    (n . zero? . branch (new const% one) (new recur% n))))

(define-class const%
  (fields run))

(define-class recur%
  (fields n)
  (define (run) 
    ((new fact%) . fact (this . n . sub1) . times (this . n))))

@@

(define true (new t%)) 
(define false (new f%))

(check-expect ((new fact%) . fact zero) one)                  ; 0! = 1
(check-expect ((new fact%) . fact one) one)                   ; 1! = 1
(check-expect ((new fact%) . fact (one . add1)) (one . add1)) ; 2! = 2
(check-expect ((new fact%) . fact (one . add1 . add1))        ; 3! = 6
              (one . add1 . add1 . add1 . add1 . add1))
\end{alltt}
\end{solution}
\end{problem}
\end{document}
